\textbackslash subsubsection\{Schema Document Properties\}
\textbackslash bf\textbackslash noindent\textbackslash emph\{Declared
Namespaces\}\} \textbackslash subsubsection\{Global Declarations\}
Complex Type: XML Instance Representation Start ChoiceCommand message
type. Requires action for receiver. Must be responded to by an
acknowledgement. Immediate response expected with deferred
processing.Acknowledgement message type. Response to CommandMessage.
Response is Accepted/Rejected.Request message type. Inquisitive for
receiver. Must be responded to by a reply. Response expected after
processing is complete. Reply message type. Response to RequestMessage.
Response is detailed.Notification message type. Asynchronous and does
not need a response or acknowledgement. Examples include heartbeat
message, log message, status message. Complex Type: CommandMessageType
XML Instance Representation Base type for a
CommandMessage.\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater{}
Schema Component Representation The UTC date and time that this message
instance was created.The sender ID of this message. This is the ID of
the component or system at which this message was formulated.The
receiver ID of this message. This is the ID of the component or system
at which this message was sent.The name for the given message type.The
actual message content, deciphered by either MessageSchemaURI or
(MessageType, MessageName, MessageVersion). Complex Type:
AcknowledgeMessageType XML Instance Representation
\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater{}
Schema Component Representation Complex Type: ReplyMessageType XML
Instance Representation Base type for a
ReplyMessage.\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater{}
Schema Component Representation Complex Type: RequestMessageType XML
Instance Representation Base type for a
RequestMessage.\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater{}
Schema Component Representation Complex Type: EventMessageType XML
Instance Representation Base type for a
EventMessage.\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater\textless\textgreater\textless/\textgreater{}
Schema Component Representation \textbackslash subsubsection\{Global
Definitions\}
